\papertitle

### 2021-03-05 source_separation/paper/paper.tex
Work on introduction

% Authors
% Please note that submissions are NOT anonymous, therefore 
% authors' names have to be VISIBLE in your manuscript. 
% Authors are entered as an ordered list, each one can be linked to multiple affiliations using the correct index.
% Available tags for authors are: \firstname \middlename \lastname \generation \originalname \email \orcid
% Available tags for affiliations are: \unit \department \institution \streetaddress \city \state \postcode \country \type
% type can take as value: University, Company, Music, Independent, Other
%
% \author[]{\mbox{\firstname{}\middlename{}\lastname{}\originalname{}\generation{}\email{}\orcid{}}}
% mbox force an author not to be split over multiple lines
\author[1]{\mbox{\firstname{Luke}\lastname{Dzwonczyk}}}
\author[1, 2]{\mbox{\firstname{L\'eo}\lastname{Chedin}}}
\author[1]{\mbox{\firstname{Alejandro}\lastname{Saldarriaga-Fuertes}}}
\author[1]{\mbox{\firstname{Max}\lastname{Sherr}}}
\author[1]{\mbox{\firstname{H\'el\`ene-Camille}\lastname{Crayencour}}}
\author[1]{\mbox{\firstname{Carmine-Emanuele}\lastname{Cella}}}

@@

	\section{Introduction}\label{sec:introduction}
	\begin{itemize}
		\item what is CAO 
		\item why we need source separation 
		\item which type of sounds are useful for us (targets)
		\item What is Orchidea?
	\end{itemize}

@@

	The approach studied in \cite{Carpentier2010} consists in finding a good orchestration for any given sound by searching combinations of sounds from a database with a multi-objective optimization heuristics and a constraint solver that are jointly optimized. Both the target sound and the sounds in the database are embedded in a feature space defined by a fixed feature function and each generated combination of sounds is evaluated by using a specific metric. This method has been substantially improved in \cite{Cella18, Cella2020} and is implemented in the \emph{Orchidea} toolbox for assisted orchestration (\url{www.orch-idea.org}), currently considered the state-of-the-art system for assisted orchestration.

	 The codebase for this paper can be found at: \url{}.

@@

	 In the field of computer-assisted composition, musical orchestration is probably the most empirical one and it has been traditionally taught in an intuitive and non formalized way. Computer-assisted orchestration seeks to help composers by accelerating certain creative processes. In particular, target-based computer-assisted orchestration helps composers to explore new timbral possibilities by associating instrumental samples, which, combined, will sound perceptually similar to a target sound. \textbf{(Note: This paragraph was moved to the intro from the abstract. We can move it back to the abstract if that would be better)}

	 Target-based computer-assisted orchestration is the process of creating an orchestral score that best matches an arbitrary target sound given a similarity metric and constraints. It recreates the timbre and harmonics of the target sound using orchestral instruments.

		Source separation is an important addition to improve orchestration as it allows for the orchestration of more complex sounds in a way that makes sense in an orchestral context. Orchestral music often uses multiple layers, so by separating the layers of a target and individually orchestrating them, the resulting solution is improved. \textbf{(@Carmine, can you make sure this paragraph makes sense/is correct?)}

@@

	\section{Methodology}\label{sec:methodology}
	Sound source separation is the process by which a single audio file is separated into multiple sound sources. A perfect separation is able to dissect a sound exactly into its constituent parts, in which each part is an independent sound event. Music source separation is specific application of sound source in which the input audio is expected to be music that is comprised of a subset of instruments or sounds. For example, one music source separation method could attempt to split a song into three parts: voice, bass, and drums. Another aimed at orchestral music may try to separate the input into families of instruments: woodwinds, brass, strings, and percussion. In contrast, universal sound separation does not operate under the assumption that the input is of a musical nature, and can be applied to arbitrary sounds. In this case, the number of sources expected is defined, and the method will attempt to divide the input into the given number of sources.

@@

	\section{Experiments}\label{sec:experiments}
	\begin{itemize}
		\item Full orchestration
		\item Ground truth
		\item NMF
		\item 4 neural models: TDCNN++, TDCNN, Demucs, OpenUnmix
		\item table with results
	\end{itemize}

@@

			\subsubsection{ConvTasNet}
			ConvTasNet \cite{tdcnn} (TDCNN) is a model based on a temporal convolutional encoder-decoder. It uses the audio waveform as input and performs a series of 1-D convolutions at different resolutions with residual connections in order to generate a pool of masks that are then applied on the embedding of the initial waveform to output the separated targets. A final 1-D convolutional layer is used as a decoder to recover the waveforms of each sub target. This type of architecture replaces RNNs in modelling sequential data, as series of dilateds convolutions are a good way to capture temporal patterns.\\

@@

			\subsubsection{Universal Sound Separation ConvTasNet}
			This version of ConvTasNet, called TDCNN++, was improved by \cite{tdcnnpp} in order to be used for general sound separation, and not only for speech. The main architecture remains the same as in \cite{tdcnn}, and the changes only affected the masking network. More specifically, feature-wise normalization replaces global normalization, residual connections ranges are extended to improve the flow of information, and learnable scale parameters are introduced to weight the outputs of each residual layer. Those modifications help the model to better extract features without drastically increasing its size.\\

@@

	\section{Conclusions}\label{sec:conclusions}
	In this paper, we addressed the problem of orchestrating dynamic targets using source separation as a preprocessing step. The results showed that performing source separation followed by a static orchestration of each individual sub targets improved the spectral distance between the original sample and its orchestrated version.\\

	Furthermore, it seems that unsupervised methods such as NMF outperform all supervised methods. However, it is important to notice that the different neural models (Demucs, ConvTasNet, ConvTasNetUniversal and OpenUnmix) were used based on pre-trained versions. Those versions were trained on musical data, except for TDCNN++ which used selected generic sound samples, which opens a large path for improvement. More specifically, we may infer from our results that models trained not only on musical data can generate a better separation for orchestration, as TDCNN++ outperforms other supervised models.\\

>>>>

% Authors
% Please note that submissions are NOT anonymous, therefore 
% authors' names have to be VISIBLE in your manuscript. 
% Authors are entered as an ordered list, each one can be linked to multiple affiliations using the correct index.
% Available tags for authors are: \firstname \middlename \lastname \generation \originalname \email \orcid
% Available tags for affiliations are: \unit \department \institution \streetaddress \city \state \postcode \country \type
% type can take as value: University, Company, Music, Independent, Other
%
% \author[]{\mbox{\firstname{}\middlename{}\lastname{}\originalname{}\generation{}\email{}\orcid{}}}
% mbox force an author not to be split over multiple lines
\author[1]{\mbox{\firstname{Luke}\lastname{Dzwonczyk}\email{dz.luke@berkeley.edu}}}
\author[1, 2]{\mbox{\firstname{L\'eo}\lastname{Chedin}}}
\author[1]{\mbox{\firstname{Alejandro}\lastname{Saldarriaga-Fuertes}}}
\author[1]{\mbox{\firstname{Max}\lastname{Sherr}}}
\author[1]{\mbox{\firstname{H\'el\`ene-Camille}\lastname{Crayencour}}}
\author[1]{\mbox{\firstname{Carmine-Emanuele}\lastname{Cella}}}

@@

	\section{Introduction}\label{sec:introduction}

@@

@@

	 In the field of computer-assisted composition, musical orchestration is probably the most empirical one and it has been traditionally taught in an intuitive and non formalized way. Computer-assisted orchestration seeks to help composers by accelerating certain creative processes. In particular, target-based computer-assisted orchestration helps composers explore new timbral possibilities by combining instrumental samples in such a way as to mimic the timbre of a given target sound. Formally, it is the process of creating an orchestral score that best matches an arbitrary target sound given a similarity metric and constraints~\cite{Maresz2003}.

	 Orchidea is a framework and set of tools that is currently considered the state-of-the-art for computer-assisted orchestration. Orchidea embeds the target in a feature space and uses a jointly-optimized multi-objective optimization heuristic and constraint solver to find a combination of samples that best match the target~\cite{Cella18, Cella2020}.

	Sound source separation is the process by which a single audio file is separated into multiple sound sources. A perfect separation is able to dissect a sound exactly into its constituent parts, in which each part is an independent sound event. Music source separation is specific application of sound source in which the input audio is expected to be music that is comprised of a subset of instruments or sounds. For example, one music source separation method could attempt to split a song into three parts: voice, bass, and drums. Another aimed at orchestral music may try to separate the input into families of instruments: woodwinds, brass, strings, and percussion. In contrast, universal sound separation does not operate under the assumption that the input is of a musical nature, and can be applied to arbitrary sounds. In this case, the number of sources expected is specified, and the method will attempt to divide the input into the given number of sources.

	Source separation is an important addition to improve orchestration as it allows for the orchestration of more complex sounds in a way that makes sense in an orchestral context. Orchestral music often uses multiple layers, so by separating the layers of a target and individually orchestrating them, the resulting solution is improved.

@@

	The codebase for this paper can be found at: \url{url needed}, and you can listen to our targets and orchestrations here: \url{url needed}.

	\section{Methodology}\label{sec:methodology}

@@

	\section{Experiments}\label{sec:experiments}

@@

			\subsubsection{ConvTasNet}
			ConvTasNet \cite{tdcnn} (TDCNN) is a model based on a temporal convolutional encoder-decoder. It uses the audio waveform as input and performs a series of 1-D convolutions at different resolutions with residual connections in order to generate a pool of masks that are then applied on the embedding of the initial waveform to output the separated targets. A final 1-D convolutional layer is used as a decoder to recover the waveforms of each sub target. This type of architecture replaces RNNs in modelling sequential data, as series of dilateds convolutions are a good way to capture temporal patterns.

@@

			\subsubsection{Universal Sound Separation ConvTasNet}
			This version of ConvTasNet, called TDCNN++, was improved by \cite{tdcnnpp} in order to be used for general sound separation, and not only for speech. The main architecture remains the same as in \cite{tdcnn}, and the changes only affected the masking network. More specifically, feature-wise normalization replaces global normalization, residual connections ranges are extended to improve the flow of information, and learnable scale parameters are introduced to weight the outputs of each residual layer. Those modifications help the model to better extract features without drastically increasing its size.

@@

	\section{Conclusions}\label{sec:conclusions}
	In this paper, we addressed the problem of orchestrating dynamic targets using source separation as a preprocessing step. The results showed that performing source separation followed by a static orchestration of each individual sub targets improved the spectral distance between the original sample and its orchestrated version.

	Furthermore, it seems that unsupervised methods such as NMF outperform all supervised methods. However, it is important to notice that the different neural models (Demucs, ConvTasNet, ConvTasNetUniversal and OpenUnmix) were used based on pre-trained versions. Those versions were trained on musical data, except for TDCNN++ which used selected generic sound samples, which opens a large path for improvement. More specifically, we may infer from our results that models trained not only on musical data can generate a better separation for orchestration, as TDCNN++ outperforms other supervised models.
